### 2019-12-28 interim/sections/background/session_types.tex
Interim write-up:  binary session types

$$
\infer[\mbox{\rulename{MTy}}]{
	\vdash \parti{p} :: P \mid 
	\parti{q} :: Q
}{
	\begin{array}{lr}
	\cdot \vdash P: S
	&
	\cdot \vdash Q: \bar{S}
	\end{array}
}
$$

@@

This motivates the concept of \term{subtypes}, which allows a process to be typed by its ``supertype'' when required. $\leqslant$ defines the subtyping relation: $S \leqslant S'$ reads \textit{$S$ is a subtype of $S'$}, and is defined coinductively.

@@

\begin{itemize}
\item \textbf{Branching}: A process can offer more branches 
\item \textbf{Selection}:
\end{itemize}

@@

We also introduce the \rulename{Ty-Sub} to incorporate the subtyping relation into the typing judgement.

@@

is well-typed, assuming the $P_\text{Client}$ and $P_\text{Server}$ are typed $S_\text{Client}$ and $S_\text{Server}$ respectively.

@@

Gentle introduction to MPST - \cite{MPST}

>>>>

$$
\infer[\mbox{\rulename{MTy}}]{
	\vdash \parti{p} :: P \mid 
	\parti{q} :: Q
}{
	\begin{array}{lr}
	\cdot \vdash P: S
	&
	\cdot \vdash Q: \overline{S}
	\end{array}
}
$$

@@

This motivates the concept of \term{subtypes}, which allows a process to be typed by its ``supertype'' when required. $\leqslant$\footnote{The $\leqslant$ operator is also an overloaded relation on sorts to express subsorting.} defines the subtyping relation: $S \leqslant S'$ reads \textit{$S$ is a subtype of $S'$}, and is defined coinductively on the structure of session types.

@@

\begin{itemize}
\item \textbf{Branching}: The supertype of a branching process offers a subset of the branches and expects more specific types of payload; intuitively, if a process expects to receive an \texttt{int}, it can handle a \texttt{nat} payload.
\item \textbf{Selection}: The supertype of a selection process offers a superset of the internal choices and can send more generic types of payload; intuitively, if a process sends a \texttt{nat}, the payload is compatible with receivers expecting a more generic \texttt{int} payload.
\end{itemize}

@@

We also introduce subsumption in \rulename{Ty-Sub} to incorporate the subtyping relation into the typing judgement.

@@

is well-typed, assuming $P_\text{Client}$ and $P_\text{Server}$ are typed $S_\text{Client}$ and $S_\text{Server}$ respectively.

@@
